Water desalination using polyelectrolyte hydrogel.

### 2022-09-01 MDPI/response_letter.tex

\item \textit{How do you think control factors in open system such as pressure and temperature}

\end{enumerate}

\textbf{Reviewer 2}
\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
\begin{enumerate}

\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
\item \textit{line 247 in what table?}
\item \textit{Where is the method of this work?}
We did not want to bother the readers too much with technical aspects of the smulations. 
The method idea is outlined in the paragraph "Physics behind the desalination process" and in the section "Theory behind the simulation". Some more technical issues are in ESI.
\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}

@@

\end{enumerate}

\textbf{Reviewer 3}

\textit{}
\begin{enumerate}
\item \textit{The full stop in the title should be revised.}
Noted. Revised.
\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
\item \textit{The manuscript must be improved by checking once again in English and technical writing. }

@@

\item \textit{The whole manuscript must be supported by enough recent references. Revise the whole context.}
\item \textit{The beginning of the introduction part must be revised to be more attractive.}
\item \textit{The authors can follow the following references to generally highlight the global contamination and environmental pollution problems at the beginning of the introduction part  \href{https://doi.org/10.1016/j.jwpe.2022.102847}{https://doi.org/10.1016/j.jwpe.2022.102847} ; \href{https://doi.org/10.1016/j.ceramint.2022.05.151}{https://doi.org/10.1016/j.ceramint.2022.05.151} ; 
\href{https://doi.org/10.3390/catal12050500}{https://doi.org/10.3390/catal12050500} ; 
\href{https://doi.org/10.1007/s11356-022-21160-7}{https://doi.org/10.1007/s11356-022-21160-7} ; 
\href{https://doi.org/10.3390/ma15134547}{https://doi.org/10.3390/ma15134547}. 
Then, highlight the water desalination technologies and Gibbs ensemble (\href{https://doi.org/10.3390/nano10020293}{https://doi.org/10.3390/nano10020293}).}
\item \textit{Authors should indicate a clear gap in knowledge which this study seeks to bridge, and potentially contribute to knowledge. }

\item \textit{L 125-126, meaningless sentence. Revise the whole context.}
\item \textit{All sections/subsections titles must be revised to be expressive.}
\item \textit{Statistical physics considerations including setup and calculations should be added.}
\item \textit{The authors should identify the limitations of this study and the recommended future studies in the conclusion part.
}
We identified the study limitations and considered the implications and future perspectives of the study. We added the respective paragraphs.
\end{enumerate}

### 2022-09-01 Creta_ecis2022/presentation/beamer.tex
presentation for ecis

\title{Modeling of weak polyelectrolyte hydrogels under compression. }
\subtitle{Implications for water desalination.}
% \date{\today}
\author{Oleg V. Rud}
\institute{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Hlavova 8, Praha 2 128 00, Czech Republic
\\
\\
Institute of Macromolecular Compounds of Russian Academy of Sciences, 199004, Bolshoy pr. 31, Saint-Petersburg, Russia
}

@@

\section[Intro]{Introduction}

\begin{frame}[fragile]{Introduction}

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=\columnwidth]{{figures/gibbs_ca}.pdf}}
			\end{figure}

		\column{0.5\textwidth}
	\begin{itemize}
		\item Desalination
		\item Hydrogels for desalination 
		\item Forward osmosis
		\item Various stimuli: thermo-, pH-, electric-, magnetic-, light-indused gel collapse
		\item Manfred Wilhelm and Yu Chi experiment
	\end{itemize}

	\end{columns}% COLUMNS
	{\scriptsize 
	Fengler, C., Arens, L., Horn, H., Wilhelm, M. (2020). {\bf Desalination of Seawater Using Cationic Poly(acrylamide) Hydrogels and Mechanical Forces for Separation.} Macromolecular Materials and Engineering\\
	Yu, C., Wang, Y., Lang, X., Fan, S. (2016). {\bf A Method for Seawater Desalination via Squeezing Ionic Hydrogels.} Environmental Science and Technology}
\end{frame}

\begin{frame}[fragile]{Donnan prediction}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.35\textwidth}
\begin{figure}
\includegraphics[height=4.5cm]{figures/gel_donnan.png}
\caption{The compression of hydrogel  affects the ionic composition of supernatant}
\end{figure}

@@

\begin{itemize}
\item Donnan equilibrium
$c_s^2 = c^{in}_{Na}\cdot c^{in}_{Cl}$
\item Electroneutrality
$\alpha N$ of self charges\\
$\alpha N$ of neutralizing counterions\\
$c^{in}_{Cl}$ of free ion pairs
\item
By compression to the dry state 
one can exclude brine of concentration
\begin{equation*}
N_{excl}/V=\begin{cases}
c_s^{in}<c_s,\\
\\
c_s^{in}+\alpha N/V_{gel}>c_s,
\end{cases}
\end{equation*}
\end{itemize}

  \end{columns}% COLUMNS

@@

>>>>

\title{Water desalination using polyelectrolyte hydrogel.  }
\subtitle{Gibbs ensemble modelling.}
% \date{\today}
\author{Oleg V. Rud}
\institute{Department of Physical and Macromolecular Chemistry, Faculty of Science, Charles University in Prague, Hlavova 8, Praha 2 128 00, Czech Republic
\\
\\
Institute of Macromolecular Compounds of Russian Academy of Sciences, 199004, Bolshoy pr. 31, Saint-Petersburg, Russia
}

@@

\section[Intro]{Introduction}
\begin{frame}[fragile]{Introduction. Desalination.}
\begin{enumerate}
\item Distillation
\item Reverse osmosis
\item Forward osmosis
\end{enumerate}
\end{frame}
\begin{frame}[fragile]{Introduction. Forward osmsis.}

\begin{enumerate}
	\item Hydrogels for desalination
	\item Forward osmosis
	\item Various stimuli: thermo-, pH-, electric-, magnetic-, light-indused gel shrinkage
\end{enumerate}
\begin{figure}[t]
	{\includegraphics[width=\columnwidth]{{figures/FO}.png}}
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Introduction. Manfred Wilhelm experiment}
	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.4\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=0.9\columnwidth]{{figures/exp}.png}}
			\end{figure}

		\column{0.6\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=0.9\columnwidth]{{figures/scheme}.png}}
			\end{figure}
	\end{columns}% COLUMNS

	{\scriptsize Fengler, C., Arens, L., Horn, H., Wilhelm, M. (2020). {\bf Desalination of Seawater Using Cationic Poly(acrylamide) Hydrogels and Mechanical Forces for Separation.} Macromolecular Materials and Engineering\\
	Yu, C., Wang, Y., Lang, X., Fan, S. (2016). {\bf A Method for Seawater Desalination via Squeezing Ionic Hydrogels.} Environmental Science and Technology}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section[Model]{Model of the gel}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Model of the gel}
  \begin{columns}[T,onlytextwidth]% COLUMNS
    \column{0.35\textwidth}
\begin{figure}
\includegraphics[height=4.5cm]{figures/gel_donnan.png}
\end{figure}

@@

\begin{itemize}
\item The gel is a particle of mAcro size 
\item In aqueous solution
\item Infinite network of polymer chains
\item Each bead is charged
\end{itemize}

  \end{columns}% COLUMNS
\begin{itemize}
\item The gel itself is a membrane
\item Donnan equilibrium
$c_s^2 = c^{in}_{Na}\cdot c^{in}_{Cl}$
\item The compression of hydrogel  affects the ionic composition of supernatant
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]{Model of the gel. Two ensembles.}

	\begin{columns}[T,onlytextwidth]% COLUMNS
		\column{0.5\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=0.9\columnwidth]{{figures/gc}.pdf}}
			\end{figure}
			\centering Open system \\(grand-cannonical ensemble)
		\column{0.5\textwidth}
			\begin{figure}[t]
				{\includegraphics[width=0.9\columnwidth]{{figures/gibbs}.pdf}}
			\end{figure}
			\centering Closed system \\(Gibbs ensemble)
	\end{columns}% COLUMNS

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
